BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC

### 2019-11-13 analysis/VOCC/4-vocc-BACI-multiyear.Rmd
plots for PICES talk

---
title: "BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Redbanded Rockfish" 
    region: "both odd year surveys"
    age: "mature"
    biomass_threshold: "50"
    climate: "temperature"
    threshold: 0.5
editor_options: 
  chunk_output_type: inline
---

@@

if (climate == "do") {
  do_threshold <- params$threshold
  root_params <- filter(root_params, lower_do_25 > 0.4)

@@

# Calculate climate vectors
```{r }
vocc_by_year <- lapply(start_years, function(start_time) {
  try({
    vocc <- readRDS(paste0(
      "data/vocc-", ssid_string, "-", climate_string, "-",
      min_string, "to", max_string, "-", start_time, "-", delta_t_total, "-update.rds"
    ))
  })

@@

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_s",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_s",
        fill_label = paste(" DO change\n", start_time, 
          "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_s",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_s",
        fill_label = paste(" DO change\n", start_time, "to", 
          start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min_do, raster_max_do),
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

all_vectors <- do.call("rbind", trimmed_vectors)

## If VOCC change is a useful column?
# all_vectors$var_1_changeA <- all_vectors$var_1_min
# all_vectors$var_2_changeA <- all_vectors$var_2_min
# all_vectors$var_1_changeB <- all_vectors$var_1_max
# all_vectors$var_2_changeB <- all_vectors$var_2_max

all_vectors$var_1_min <- lower_thresholds[1]
all_vectors$var_2_min <- lower_thresholds[2]
all_vectors$var_1_max <- upper_thresholds[1]
all_vectors$var_2_max <- upper_thresholds[2]

if (climate == "temperature") {
  all_vectors$diff <- all_vectors$units_per_decade / 10 * delta_t_total
  # raster_min <- min(all_vectors$diff)
  # raster_max <- max(all_vectors$diff)
  raster_min <- quantile(all_vectors$diff, 0.005)
  raster_max <- quantile(all_vectors$diff, 0.995)
}

if (climate == "do") {
  all_vectors$diff <- all_vectors$units_per_decade / 10 * delta_t_total
  # raster_min <- min(all_vectors$diff)
  # raster_max <- max(all_vectors$diff)
  # 
  raster_min <- quantile(all_vectors$diff, 0.0005)
  raster_max <- quantile(all_vectors$diff, 0.9995)

@@

if (climate == "do and temperature") {
  all_vectors$temp_diff <- all_vectors$temp.units_per_decade / 10 * delta_t_total
  all_vectors$do_diff <- all_vectors$do_est.units_per_decade / 10 * delta_t_total
  raster_min_temp <- min(all_vectors$temp_diff)
  raster_max_temp <- max(all_vectors$temp_diff)
  raster_min_do <- min(all_vectors$do_diff)
  raster_max_do <- max(all_vectors$do_diff)
}
```

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "#9E0142",
        # mid_fill = NULL, #"#FFFEC9", #cream
        # high_fill = "#D53E4F",#"Steel Blue 4"
        # low_fill = "#5E4FA2",
        white_zero = TRUE,
        vec_col = "white",
        vec_alpha = 0.45,
        axis_lables = FALSE,
        transform_col =  sqrt #fourth_root_power
      ) + ggtitle(climate) #+ ggpubr::theme_transparent()# +  theme_black()
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt# no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        white_zero = TRUE,
        high_fill = "Steel Blue 3",
        low_fill = "Red 2",
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("do")

@@

### Plot remaining climate vectors for regions where change exceeds thresholds
```{r echo=FALSE, warning=FALSE}

@@

      vocc_plot <- plot_vocc(vectors,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot <- plot_vocc(vectors,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot_temp <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        na_colour = "gray",
        white_zero = TRUE,
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vectors,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

```{r}
png(
  file = paste0(
    "figs/", spp,
    "/vocc-", min_string, "to", max_string, "-",
    climate_string, "-", spp, "-", age, "-", ssid_string, "-perc_", biomass_threshold, "-", optimal_string, "-allpairs-test.png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = trimmed_vector_plots,
  ncol = 2,
  top = grid::textGrob(paste("Vectors for cells exceeding", climate, "threshold of", optimal_string, "\n based on", biomass_threshold, "percent of maximum predicted", species, "biomass (", trim_models, ")"), gp = grid::gpar(fontsize = 16))
)
dev.off()
```

@@

# keep just one row for each cell that exceeded the end climate threshold
# FIXME: this code could/maybe should be rewritten with an if_else mutate and then distinct...
source_cells <- all_vectors %>%
  filter(distance > (-dist_intercept)) %>%
  distinct(icell, start_time, .keep_all = TRUE) %>%
  select(-target_X, -target_Y, -target_values, -tid)

@@

# identify all possible control cells have been given a distance == - dist_intercept
control_cells <- all_vectors %>%
  filter(distance == (-dist_intercept)) %>%
  distinct(icell, start_time, .keep_all = TRUE) %>%
  mutate(distance = (-dist_intercept)) %>%
  select(-target_X, -target_Y, -target_values, -tid)

@@

alldata <- rbind(source_biomass, control_biomass)
alldata <- mutate(alldata, treat = ifelse(cell_type == "source", 1, 0)) %>%
  select(-mean_target_X, -mean_target_Y) %>%
  rename(vect_dist = distance)
alldata$treat <- as.factor(alldata$treat)

if(is.na(alldata$var_1_max[2])) {
  alldata <- alldata %>% select(-var_1_max)
}
if(is.na(alldata$var_1_min[2])) {
  alldata <- alldata %>% select(-var_1_min)
}
if(is.na(alldata$var_2_max[2])) {
  alldata <- alldata %>% select(-var_2_max)
}
if(is.na(alldata$var_2_min[2])) {
  alldata <- alldata %>% select(-var_2_min)
}
# alldata
# })
```

@@

# set limits same for all years based on percent change for cells with vectors
# raster_min <- min((log(alldata$end_density+1)-log(alldata$start_density+1)))
# raster_max <- max((log(alldata$end_density+1)-log(alldata$start_density+1)))
raster_min <- quantile(((alldata$end_density)-(alldata$start_density)), 0.01)
raster_max <- max((alldata$end_density)-(alldata$start_density))#, 0.9999)

@@

    vocc_plot <- plot_vocc(biomass,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "density_diff",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        # varidis_option = 
        white_zero = FALSE,
        # mid_fill = NULL,
        # high_fill = "#5E4FA2", #"Steel Blue 4"
        # low_fill = "#D53E4F",
        # high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        # low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"   
        na_colour = "red",
        vec_col = "white",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col =  sqrt # no_trans ##fourth_root_power #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))

@@

### Plot climate vectors for cells with starting with greater than 25% percentile of biomass densities
```{r echo=FALSE, warning=FALSE}
# # set lower_density_threshold of cells with cumulative densities of less than 5% of peak biomass across years
bio5perc <- sum(biomass_change$start_density)*0.05
s <- sort(biomass_change$start_density)
bio_sum <- cumsum(s)
lower_density_threshold <- s[which(bio_sum>bio5perc)[1]]

@@

```{r}

biomass_vector_plots_trim <- lapply(trimmed_vectors, function(vectors) {
  try({
    # #offset vectors so that they represent the time step before the one for biomass change
    # vectors <- vectors %>% mutate(start_time = start_time + 2, end_time = end_time + 2)

>>>>

---
title: "BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Redbanded Rockfish" 
    region: "both odd year surveys"
    #region: "West Coast Vancouver Island"
    age: "mature"
    biomass_threshold: "50"
    climate: "temperature"
    threshold: 0.25
editor_options: 
  chunk_output_type: inline
---

@@

if (climate == "do") {
  do_threshold <- params$threshold

   if (threshold) { do_threshold <- params$threshold } else {
  do_threshold <- root_params[rev(order(root_params$do_maxy)), ]$upper_do_50 - root_params[rev(order(root_params$do_maxy)), ]$upper_do_75
  do_threshold <- round(do_threshold, 2)
  }

  root_params <- filter(root_params, lower_do_25 > 0.4)

@@

# Calculate climate vectors
```{r }
vocc_by_year <- lapply(start_years, function(start_time) {
  # try({
  #   vocc <- readRDS(paste0(
  #     "data/vocc-", ssid_string, "-", climate_string, "-",
  #     min_string, "to", max_string, "-", start_time, "-", delta_t_total, "-update.rds"
  #   ))
  # })

@@

  all_vectors <- do.call("rbind", vocc_by_year[3:7])

  raster_min <- min(all_vectors$temp_e)
  raster_max <- max(all_vectors$temp_e)

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        # theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        # theme = "black",
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_e",
        fill_label = paste(" DO change\n", start_time, 
          "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc, 
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min_temp, raster_max_temp),
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,  
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_e",
        fill_label = paste(" DO change\n", start_time, "to", 
          start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min_do, raster_max_do),
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

all_vectors_trim <- do.call("rbind", trimmed_vectors)

## If VOCC change is a useful column?
# all_vectors_trim$var_1_changeA <- all_vectors_trim$var_1_min
# all_vectors_trim$var_2_changeA <- all_vectors_trim$var_2_min
# all_vectors_trim$var_1_changeB <- all_vectors_trim$var_1_max
# all_vectors_trim$var_2_changeB <- all_vectors_trim$var_2_max

all_vectors_trim$var_1_min <- lower_thresholds[1]
all_vectors_trim$var_2_min <- lower_thresholds[2]
all_vectors_trim$var_1_max <- upper_thresholds[1]
all_vectors_trim$var_2_max <- upper_thresholds[2]

if (climate == "temperature") {
  all_vectors_trim$diff <- all_vectors_trim$units_per_decade / 10 * delta_t_total
  # raster_min <- min(all_vectors_trim$diff)
  # raster_max <- max(all_vectors_trim$diff)
  raster_min <- quantile(all_vectors_trim$diff, 0.005)
  raster_max <- quantile(all_vectors_trim$diff, 0.995)
}

if (climate == "do") {
  all_vectors_trim$diff <- all_vectors_trim$units_per_decade / 10 * delta_t_total
  # raster_min <- min(all_vectors_trim$diff)
  # raster_max <- max(all_vectors_trim$diff)
  # 
  raster_min <- quantile(all_vectors_trim$diff, 0.0005)
  raster_max <- quantile(all_vectors_trim$diff, 0.9995)

@@

if (climate == "do and temperature") {
  all_vectors_trim$temp_diff <- all_vectors_trim$temp.units_per_decade / 10 * delta_t_total
  all_vectors_trim$do_diff <- all_vectors_trim$do_est.units_per_decade / 10 * delta_t_total
  raster_min_temp <- min(all_vectors_trim$temp_diff)
  raster_max_temp <- max(all_vectors_trim$temp_diff)
  raster_min_do <- min(all_vectors_trim$do_diff)
  raster_max_do <- max(all_vectors_trim$do_diff)
}
```

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "#9E0142",
        # mid_fill = NULL, #"#FFFEC9", #cream
        # high_fill = "#D53E4F",#"Steel Blue 4"
        # low_fill = "#5E4FA2",
        white_zero = TRUE,
        vec_col = "white",
        vec_alpha = 0.45,
        axis_lables = FALSE,
        transform_col =  sqrt #fourth_root_power
      ) + ggtitle(climate) #+ ggpubr::theme_transparent()# +  theme_black()
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt# no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc,  
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,  
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        white_zero = TRUE,
        high_fill = "Steel Blue 3",
        low_fill = "Red 2",
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("do")

@@

### Plot remaining climate vectors for regions where change exceeds thresholds
```{r , eval=FALSE, echo=FALSE, warning=FALSE}

@@

      vocc_plot <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot_temp <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        na_colour = "gray",
        white_zero = TRUE,
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

```{r, eval=FALSE}
png(
  file = paste0(
    "figs/", spp,
    "/vocc-", min_string, "to", max_string, "-",
    climate_string, "-", spp, "-", age, "-", ssid_string, "-perc_", biomass_threshold, "-", optimal_string, "-allpairs-test.png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = trimmed_vector_plots,
  ncol = 2,
  top = grid::textGrob(paste("Vectors for cells exceeding", climate, "threshold of", optimal_string, "\n based on", biomass_threshold, "percent of maximum predicted", species, "biomass (", trim_models, ")"), gp = grid::gpar(fontsize = 16))
)
dev.off()
```

@@

# keep just one row for each cell that exceeded the end climate threshold
# FIXME: this code could/maybe should be rewritten with an if_else mutate and then distinct...
source_cells <- all_vectors_trim %>%
  filter(distance > (-dist_intercept)) %>%
  distinct(icell, start_time, .keep_all = TRUE) %>%
  select(-target_X, -target_Y, -target_values, -tid)

@@

# identify all possible control cells have been given a distance == - dist_intercept
control_cells <- all_vectors_trim %>%
  filter(distance == (-dist_intercept)) %>%
  distinct(icell, start_time, .keep_all = TRUE) %>%
  mutate(distance = (-dist_intercept)) %>%
  select(-target_X, -target_Y, -target_values, -tid)

@@

alldata <- rbind(source_biomass, control_biomass)
alldata <- mutate(alldata, treat = ifelse(cell_type == "source", 1, 0), dist_x_biomass_s = start_density*distance, dist_x_biomass_e = end_density*distance) %>%
  select(-mean_target_X, -mean_target_Y) %>%
  rename(vect_dist = distance)
alldata$treat <- as.factor(alldata$treat)

alldata <- alldata %>% group_by(start_time) %>% mutate(
  start_total_biomass = sum(start_density), 
  end_total_biomass = sum(end_density),
  sum_weighted_dist = sum(dist_x_biomass_s),  
  ann_climate_pressure = sum_weighted_dist/start_total_biomass)

pressure <- unique(alldata$ann_climate_pressure)
start_biomass <- unique(alldata$start_total_biomass)
end_biomass <- unique(alldata$end_total_biomass)
score_year <- unique(alldata$start_time) + 2

scores <- as.data.frame(cbind(score_year, pressure, start_biomass, end_biomass))

if(is.na(alldata$var_1_max[2])) {
  alldata <- alldata %>% select(-var_1_max)
}
if(is.na(alldata$var_1_min[2])) {
  alldata <- alldata %>% select(-var_1_min)
}
if(is.na(alldata$var_2_max[2])) {
  alldata <- alldata %>% select(-var_2_max)
}
if(is.na(alldata$var_2_min[2])) {
  alldata <- alldata %>% select(-var_2_min)
}
# alldata
# })

ggplot(scores, aes(pressure, (end_biomass-start_biomass), colour = as.factor(score_year))) + 
  geom_point(size =3) + 
  #geom_point(aes(end_biomass, pressure, colour = as.factor(score_year)), 
    #shape = 1, size = 3) + 
  scale_colour_viridis_d()

print(scores)
```

@@

# set limits same for all years based on percent change for cells with vectors
# raster_min <- min((log(alldata$end_density+1)-log(alldata$start_density+1)))
# raster_max <- max((log(alldata$end_density+1)-log(alldata$start_density+1)))
# raster_min <- quantile(((alldata$end_density)-(alldata$start_density)), 0.01)
# raster_max <- max((alldata$end_density)-(alldata$start_density))#, 0.9999)

@@

    raster_min <- min(biomass$density_diff) #, 0.01)
    raster_max <- -(raster_min)#, 0.9999)

    vocc_plot <- plot_vocc(biomass,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "density_diff",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        # varidis_option = 
        #white_zero = FALSE,
        white_zero = TRUE,
        mid_fill = "black",
        high_fill = "#66C2A5", #"Steel Blue 4", "#3288BD", #
        low_fill = "#5E4FA2FF", #"Red",
        # high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        # low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"   
        na_colour = "#66C2A5", #"3288BD", #"Steel Blue 4",
        vec_col = "white",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col =  fourth_root_power #sqrt # no_trans ##
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" )) #+ theme_black()

@@

### Plot all climate vectors against biomass
```{r echo=FALSE, warning=FALSE}
# # set lower_density_threshold of cells with cumulative densities of less than 5% of peak biomass across years
bio5perc <- sum(biomass_change$start_density)*0.05
s <- sort(biomass_change$start_density)
bio_sum <- cumsum(s)
lower_density_threshold <- s[which(bio_sum>bio5perc)[1]]

@@

### Trim for vectors on cells accounting for 95% of biomass
```{r echo=FALSE, warning=FALSE}
# # set lower_density_threshold of cells with cumulative densities of less than 5% of peak biomass across years
bio5perc <- sum(biomass_change$start_density)*0.05
s <- sort(biomass_change$start_density)
bio_sum <- cumsum(s)
lower_density_threshold <- s[which(bio_sum>bio5perc)[1]]
